Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Finishing revision of the state of the art

To better train and test agents, more
novel and some times, challenging levels must be generated. Stephenson et
al. proposed a related competition \cite{Stephenson2018} this time with the goal of developing a
level generator for the game. Researchers have proposed several generators
in the following years of competition. M. Katina et al. In Kaidan's model \cite{Kaidan2015}, the algorithm controls the generation of content by
using the skill of a player, while she is actively playing the game; The
moment the player finishes a certain level, the algorithm obtains the score
and generates the next level to play. The model proposed by Stephenson and Renz \cite{DBLP:journals/corr/abs-1902-02518} also adapts itself to the level of difficult that's needed.

>>>>

To better train and test agents, more
novel and some times, challenging levels must be generated. Stephenson et
al. proposed a related competition \cite{Stephenson2018} this time with the goal of developing a
level generator for the game. Researchers have proposed several generators
in the following years of competition. M. Katina et al. In Kaidan's model \cite{Kaidan2015}, the algorithm controls the generation of content by
using the skill of a player, while she is actively playing the game; The
moment the player finishes a certain level, the algorithm obtains the score
and generates the next level to play. The model proposed by Stephenson and Renz \cite{DBLP:journals/corr/abs-1902-02518} also adapts itself to the level of difficult that's needed. Initial papers \cite{8080448} contained search-based PCGs that established certain patterns in the structure, and assigned blocks to them, looking to optimize overall stability, but also creating a complex fitness function that included several {\em colored} scores that considered how pigs were protected, for instance.
